This paper introduces a novel platform for cloud computing where independent entities, referred to as 'node providers', supply hardware resources to developers in exchange for monetary compensation in a decentralized manner. The proposed platform addresses several challenges inherent to conventional centralized cloud computing, such as security, privacy, trust, resource allocation, and vendor lock-in. Additionally, it overcomes certain limitations of existing decentralized cloud computing platforms by offering native performance familiar to traditional developers and a reputation tracking system that mitigates the risks of malicious behavior, if desired by the developer.

The system supports sensitive data processing and storage using Confidential Computing VMs, incorporating robust data protection measures to secure sensitive information. Developers can select VMs based on their specific needs and preferences and can easily switch between node providers. To ensure stability and reliability, resilience measures are integrated into the system.

The platform also facilitates the rental of GPU nodes for Machine Learning (ML) and Artificial Intelligence (AI) training and inference applications at reasonable market prices, catering to different developer preferences. Some developers may opt for the lowest cost GPUs irrespective of node provider reputation and confidentiality guarantees, while others may prefer high-end GPUs with higher node provider reputation. This flexibility accommodates all developer categories, a feature unique to this platform.

A decentralized service running on a blockchain facilitates the connection between developers and node providers. From the blockchain information, developers can filter available resources based on requirements such as the number of nodes, computational resources, storage needs, network conditions, and the desired reputation of nodes and node providers.

Our goal is not merely to create a secure, efficient, and trustworthy decentralized cloud computing system. The platform enables honest node providers to quickly find paying customers and succeed. With robust safeguards, individuals and companies can monetize otherwise idle computing power safely. The platform's reputation tracking system helps mitigate the risks of malicious behavior, if desired by the developer.

Moreover, Decent Cloud significantly enhances the Developer Experience compared to conventional web3 platforms. Typically, running on web3 requires developers to reengineer and rewrite legacy applications, a daunting task for many. On Decent Cloud, users can run conventional applications directly, without modifications. Only the critical and latency-insensitive components (the control path), specifically reputation and financial transactions, operate on a decentralized blockchain. This division of responsibility provides developers with the conventional performance and flexibility of web2 while offering substantial security features intrinsic to web3.
